Concurrent Programming in Harmony

### 2021-01-31 book/paper.tex
Some fixes

If the threads run one at a time, then \textit{count} will be incremented
twice and ends up being 2.  However, the following is also
a possible interleaving of \texttt{incrementer(0)} and \texttt{incrementer(1)}:
\begin{enumerate}
\item \texttt{incrementer(0)} loads the value of \textit{count}, which is 0;
\item \texttt{incrementer(1)} loads the value of \textit{count}, which is still 0;
\item \texttt{incrementer(1)} adds one to the value that it loaded (0), and
stores $1$ into \textit{count};
\item \texttt{incrementer(0)} adds one to the value that it loaded (0), and
stores $1$ into \textit{count};
\item \texttt{incrementer(0)} sets \textit{done}[0] to \texttt{True};
\item \texttt{incrementer(1)} sets \textit{done}[1] to \texttt{True}.
\end{enumerate}

>>>>

If the threads run one at a time, then \textit{count} will be incremented
twice and ends up being 2.  However, the following is also
a possible interleaving of \texttt{incrementer(0)} and \texttt{incrementer(1)}:
\begin{enumerate}
\item \texttt{incrementer(0)} loads the value of \textit{count}, which is 0;
\item \texttt{incrementer(1)} loads the value of \textit{count}, which is still 0;
\item \texttt{incrementer(1)} adds 1 to the value that it loaded (0), and
stores $1$ into \textit{count};
\item \texttt{incrementer(0)} adds 1 to the value that it loaded (0), and
stores $1$ into \textit{count};
\item \texttt{incrementer(0)} sets \textit{done}[0] to \texttt{True};
\item \texttt{incrementer(1)} sets \textit{done}[1] to \texttt{True}.
\end{enumerate}
